---
title: "P8105 Homework 3"
author: "Junhui Mi"
date: "2019/11/9"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%")

library(tidyverse)
library(ggridges)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

# Problem 1

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

replace_missing = function(x) {
    if (is.numeric(x)) {
    x[is.na(x)] = mean(x, na.rm = TRUE)
      }
    x[is.na(x)] = "virginica"
    x
}

iris_without_missing_list = map(iris_with_missing, replace_missing)

iris_without_missing_tibble = map_dfr(iris_with_missing, replace_missing)

iris_without_missing_tibble
```

This function replaces missing values in "iris_with_missing". "iris_without_missing_list" returns a list of 5, while "iris_without_missing_tibble" turns the list into a tibble.

# Problem 2

```{r}
filename = list.files("./data") %>% as_tibble()

con_exp = list.files("./data", full.names = TRUE)

load_and_tidy = function(path) {
  df = read_csv(path) %>%
    janitor::clean_names() %>%
    mutate(
        arm = str_sub(path, 8, 10),
        id = str_sub(path, 12, 13),
        arm = str_replace_all(arm, c("con" = "control", "exp" = "experiment"))) %>%
    select(id, arm, week_1:week_8)
  df
}

observation_data = map_df(.x = con_exp, ~ load_and_tidy(.x))

observation_data

observation_data %>%
  gather(key = week, value = observation, week_1:week_8) %>%
  mutate(week = str_replace(week, "week_", "")) %>%
  ggplot(aes(x = week, y = observation, color = id, group = id)) +
  geom_point() + geom_line() + facet_grid(~arm) + 
  labs(title = "Spaghetti Plot of Experiment Arms and Control Arms")
```

Comment:

From the plot above we can see that data in control group does not change over time, but experimental group data increases significantly over time.

# Problem 3

Generate datasets
```{r}
set.seed(1)

sim_regression = function(n = 30, beta0 = 2, beta1) {
  
  sim_data = tibble(
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(30, 0, sqrt(50))
  )
  
  ls = lm(y ~ x, data = sim_data)
  
  tibble(
    beta1_hat = coef(ls)[2],
    p_value = pull(broom::tidy(ls),p.value)[[2]]
  )
}

output = 
  tibble(beta1_value = c(0:6)) %>% 
  mutate(
    output_list = map(.x = beta1_value,
                      ~rerun(10000, sim_regression(beta1 = .x))),
    estimate_df = map(output_list, bind_rows)) %>% 
  select(-output_list) %>% 
  unnest(estimate_df)
```

```{r}
output %>% 
  filter(p_value < 0.05) %>%
  group_by(beta1_value) %>%
  summarize(proportion = n()/10000) %>%
  ggplot(aes(x = beta1_value, y = proportion)) + 
    geom_point() + geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = c(0,1,2,3,4,5,6)) +
  geom_text(aes(label = round(proportion, digits = 2))) +
  labs(title = "Association between effect size and power", 
       x = "true value of beta1",
       y = "proportion of rejected nulls")
```

Comment:

From the plot we can see that as beta1 true value increases, the proportion of rejecting the nulls increases. Effect size is equal to (beta1 - 0)/sd. This means that as effect size increases, power of the test increases. 

```{r}
beta1_estimate = output %>%
  group_by(beta1_value) %>%
  summarize(average_beta1_hat = mean(beta1_hat))

ggplot(data = beta1_estimate,
       aes(x = beta1_value, y = average_beta1_hat)) + 
    geom_point() + geom_smooth(se = FALSE) +
  scale_x_continuous(breaks = c(0,1,2,3,4,5,6)) +
  scale_y_continuous(breaks = c(0,1,2,3,4,5,6)) +
  geom_text(aes(label = round(average_beta1_hat, digits = 2))) +
  labs(title = "Plot of beta1 estimation", 
       x = "true value of beta1",
       y = "average estimation of beta1")

output %>%
  filter(p_value < 0.05) %>%
  group_by(beta1_value) %>%
  summarize(average_beta1_hat_rejected = mean(beta1_hat)) %>%
  ggplot(aes(x = beta1_value,
             y = average_beta1_hat_rejected)) + 
    geom_point(color = 2) + geom_smooth(se = FALSE) +
  geom_point(data = beta1_estimate,
             y = pull(beta1_estimate, average_beta1_hat),
             color = "black") +
  scale_x_continuous(breaks = c(0,1,2,3,4,5,6)) +
  scale_y_continuous(breaks = c(0,1,2,3,4,5,6)) +
  geom_text(aes(label = round(average_beta1_hat_rejected, digits = 2))) +
  labs(title = "Plot of beta1 estimation which the null was rejected", 
       x = "true value of beta1",
       y = "average estimation of beta1 which the null was rejected")
```

Comment:

The first plot shows the association between the average estimate of beta1 and the true value of beta1, while the second plot shows the association between average estimate of beta1 only in samples for which the null was rejected and true value of beta1.

According to the first plot, the average of estimated beta1 for all sample is close to the true value of beta1 whatever beta1 is.

According to the second plot, the average estimate of beta1 only in samples for which the null was rejected is farer from true beta1 if beta1 is small(0,1,2) and closer to true beta1 if beta1 becomes larger(4,5,6).

The reason is that when effect size is small, the proportion of rejection is small, so the average estimate of beta1 only in samples for which the null was rejected will be far from the true value. When the effect size is large, then the proportion of rejection is large, so the average estimate of beta1 only in samples for which the null was rejected will become closer to the true value.